
\documentclass[a4paper,10pt]{article}
\usepackage{latexsym}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{geometry}
\usepackage{hyperref}
\usepackage{parskip}
\usepackage{mathpazo}
\setlength{\parskip}{0pt}
\geometry{top=0.75in, bottom=0.75in, left=0.7in, right=0.7in}

\titleformat{\section}{\large\bfseries}{}{0em}{}[\titlerule]
\pagenumbering{gobble}

\begin{document}

\begin{center}
    {\LARGE \textbf{Cody McKeon}} \\
    \vspace{4pt}
    Lake Havasu City, AZ \\
    \href{mailto:codymckeon@gmail.com}{codymckeon@gmail.com} | (760) 669-9343 | \href{https://github.com/cody-mckeon}{github.com/cody-mckeon}
\end{center}

\vspace{8pt}

\section*{Summary}
Tech-savvy professional with a strong background in project management and marketing technology, recently transitioned into Data Science. Led a full-stack MLOps project with a focus on data versioning, model tracking, explainability, and deployment. Adept at applying ML pipelines in practical business contexts using modern open-source tools.

\section*{Experience}

\textbf{Data Scientist (Contract)} \hfill Nov 2022 -- Present \\
\textit{Independent Project | Hilton-Style MLOps Pipeline} \\
\begin{itemize}[leftmargin=*, itemsep=2pt, parsep=0pt]
    \item Led the end-to-end development of a machine learning model to predict guest upsell propensity and forecast revenue.
    \item Implemented data versioning and transformation pipelines using DVC with raw/processed Parquet datasets.
    \item Built and tracked classification/regression models using XGBoost; logged runs, metrics, and artifacts with MLflow.
    \item Achieved ROC AUC of 0.713 and reduced MAE to \$1.52 using Optuna for hyperparameter optimization.
    \item "Generated SHAP insights on lead time, booking source, and deposit type.
    \item Deployed model as a FastAPI microservice containerized in Docker and published to GitHub Container Registry (GHCR) via CI/CD.
    \item Added drift detection automation using Evidently and planned model retraining triggers.
\end{itemize}

\textbf{Business Analyst} \hfill 2023 -- Present \\
\textit{Lake Havasu City} \\
\begin{itemize}[leftmargin=*, itemsep=2pt, parsep=0pt]
    \item Led needs assessments and process analyses across public safety departments to scope and onboard vendor software.
    \item Translated operational challenges into business and technical requirements across IT, police, and fire.
    \item Presented findings and data dashboards to city stakeholders to drive adoption and track KPIs.
\end{itemize}

\textbf{Product Marketing Manager} \hfill 2018 -- 2023 \\
\textit{Walmart Global eCommerce} \\
\begin{itemize}[leftmargin=*, itemsep=2pt, parsep=0pt]
    \item Managed high-throughput digital campaigns targeting members across Walmart platforms.
    \item Collaborated with engineering teams on feature delivery for marketing APIs and ad tech integrations.
\end{itemize}

\section*{Projects}

\textbf{Vacation Ownership Demand Forecasting (MLOps Case Study)} \\
\begin{itemize}[leftmargin=*, itemsep=2pt, parsep=0pt]
    \item Simulated upsell and revenue forecasts on hotel data using XGBoost and SHAP.
    \item Deployed MLOps stack with FastAPI, Docker, GHCR, and drift monitoring.
\end{itemize}

\subsection*{High-Probability Options Screener}
\begin{itemize}[leftmargin=*, itemsep=2pt, parsep=0pt]
    \item Ranked options using POP, IV, and earnings signals.
    \item Engineered strategy rules and visualized PnL histograms.
\end{itemize}

\section*{Skills}
\begin{tabular}{p{0.25\textwidth} p{0.7\textwidth}}
\textbf{Languages/Tools} & Python, SQL, Git, Bash, Markdown \\
\textbf{ML/Data} & XGBoost, pandas, scikit-learn, Optuna, SHAP, Evidently \\
\textbf{Ops} & DVC, MLflow, Docker, FastAPI, GitHub Actions \\
\end{tabular}


\section*{Education}

\textbf{B.A. in Computer Science} \hfill University of Nevada Las Vegas \hfill 2018

\end{document}
